### 2023-11-09 manuscript/manuscript.Rmd
fix sentence grammar for Figure 3 reference

As shown in Figure \@ref(fig:figure-3-feature-solutions), there can be multiple graphical molecular formula component solutions can exist for a given *m/z* feature.
The component plausibility score was the primary criterion for which components were selected. 
This score combines information about how connected the features are within a given component, the average strength of these connections and the expected commonality of the adduct and isotopic combinations present.
By using this information about the connections of *m/z* within the spectrum, it is possible for an *m/z* to be assigned a less plausible molecular formula if it is more highly connected with strong connections containing more common adduct and isotopic combinations.
Combining information between the ionisation modes further increases available information and more informative components [@kuhl2012].

>>>>

As shown in Figure \@ref(fig:figure-3-feature-solutions), there can be multiple graphical component solutions that can exist for a given *m/z* feature.
The component plausibility score was the primary criterion for which components were selected. 
This score combines information about how connected the features are within a given component, the average strength of these connections and the expected commonality of the adduct and isotopic combinations present.
By using this information about the connections of *m/z* within the spectrum, it is possible for an *m/z* to be assigned a less plausible molecular formula if it is more highly connected with strong connections containing more common adduct and isotopic combinations.
Combining information between the ionisation modes further increases available information and more informative components [@kuhl2012].
